---
title: "Com_qual_v1"
author:
- Sina Özdemir^[PhD Candidate, Department of Sociology and Political Science, Norwegian
  University of Science and Technology]
- Christian Rauh^[Prof., Global Governance Unit, Social Science Center Berlin]
date: "5/14/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packs<- c("tidyverse","igraph","kableExtra")
library(pacman)
pacman::p_load(char = packs)
data.eu<- readRDS(file = "C:/Users/sinaoz/OneDrive - NTNU/Projects/communication_quality_repo/data/corpii/EU_analysis_data.RDS")
```

# Introduction

## Para 1: 

- the EU is irreversably policitised. Its legitimacy is challenged on many fronts

## Para 2:

- The EU has internal and external problems with communicating its legitimacy

## Para 3:

- Social media offers unique solutions to external communication problems

## Para 4:

- What we do in the article
 
## Para 5: 

- Organization of the article

# Legitimacy deficit of the EU

## Para 1:

- Introduction: what kind of legitimacy problem

## Para 2:

- Legitimacy deficit: input legitimacy

## Para 3:

- Legitimacy deficit: output legitimacy

## Para 3: 

- Legitimacy deficit: throughput legitimacy

## Para 4:

- Legitimacy deficit: communication deficit

# Public communication and the EU's legitimacy

## Para 1:

- Communication deficit: internal problems

## Para 2: 

- Communication deficit: external problems

## Para 3:

- Attempts at remedying communication deficit

## Para 4:

- How can public communication via social media help with legitimacy deficit

    - Meritocratic legitimacy (Meyer 1999)
    
    - SoMe: direct communication with citizens, thus a solution to external communication problems
    
    - Volume: telling what the EU does helps with output legitimacy
    
    - Ease-of-reade: makes the EU politics comprehensible
    
    - Interactivity: build connection with the audience so that audience feels heard
    
    - Political responsiblity reporting: Helps with transparency, because now the audience knows who is responsible for what
    
    

# Data and method

## Data

We follow a purposeful sampling strategy and target historical tweets from 115 verified Twitter accounts of the EU to investigate the communication performance of the EU on social media. The accounts cover the supranational institutions of the EU, their sub-branches such as agencies, and individuals who are in charge of these institutions such as commissioners, and director generals. Graph 1 gives an overview of the account type and tweet volume. Full list of accounts and descriptions is presented in Appendix(X).

The motivation behind choosing these accounts is two-folds. First of all, the selection of accounts collectively reflect branches of the EU that exercise political authority as a polity. Thus giving us a clear picture of the EU's public communication as a polity[CITATION HERE]. Secondly, extant research shows that executive branches of the EU (i.e supranational institutions) such as the Commission and the ECB, are often the core subjects of politicization in national media. Thus, it is often their institutional legitimacy that is questioned and equated with the overall legitimacy of the EU in citizens mind[@Silvia2021]. 

We target three sets of accounts to benchmark the EU's communication quality on social media namely. The first set of accounts belong to the international organizations (IOs) which are comparable to the EU in terms of policy scope. Research shows that one of the key determinants of politicization of international political authority is breadth of the policy scope of said authority[@Rauh2019;@Zuern2018;@DeWilde2011]. While no other international organization has breadth and depth of political authority as EU, the selected international organizations are most similar to the EU in terms of number of policy areas. To identify and select these accounts, we make use of "Measuring International Authority" by Marks, Hooghie and Lenz[-@Hooghe2021] dataset. The number of policy area responsibilities of these international organization are approximately 1 sd around the EU's number of policy area responsibilities. List of organizations and Twitter accounts are presented in the Appendix(X).

The second set of benchmark accounts belongs the UK government. More specifically, we target the current UK government ministers, ministries, executive offices, agencies and individuals who are in charge of these institutions. As aptly named by Jacques Delore, the EU is a unidentified political object [couldn't remember the French spelling]. On the one hand, its competencies approximate that of a nation state. On the other hand, it carries significant markers of an international organization where member states guide and decide on how the political authority will be exercised. Thus, making the EU neither a fully sovereign political authority nor a platform for sovereigns to collaborate together. Due to this nature of the EU, we choose to benchmark the EU's public communication on Twitter against that of national government. However, due to resource limitations to analyze wide variety of national languages, we focus on the UK government.

Our last set of benchmark is a random set of tweets from the EU countries. We streamed in tweets from 26 of the EU countries for a week with 5 min. windows. Our motivation is to identify a baseline for syntactic feature of communication in Twitter environment in the EU.

We collect historical data from the EU, the UK and IOs using Twitter API 2.0 academic track. The total amount of data amounts up to [**TOTAL NUMBER OF TWEETS HERE**] where `r nrow(data.eu)` is from the EU accounts, [**nrow uk here**] is from the UK accounts and [**nrow io here**] from IO accounts. The streamed tweets are collected using Twitter decahose API as this end-point was not available with API 2.0 famility at time of collection.

## Method
To examine the communication of quality we focus on three sets of indicators; readability, interactivity and reporting of political responsibility. To measure readability of the tweets, we create several measures focusing on syntactic features of the tweet. Table 1 presents these indicators. [**Christian writes something here about the preprocessing steps**]. We measure interactivity as percentage share of quotes, retweets and replies per account. Lastly, we approximate political responsibility reporting by combining part-of-speech tagging and dictonary method. First we identify tweets reporting on policy issues using dictionary from Comparative Agendas Project [CAP citation here]^[**I haven't managed to find the dictionary yet. This method also needs to be validated manually later on**]. We then identify tweets that contain responsibility attributing grammar structure among the policy issue related tweets using part of speech tagging^[responsbility attribution grammar follows "Noun"or"Personal Pronoun" + "Action verb" structure].

# Results and discussion

##Broad overview of the data

## Within sample comparision: communication performance of different EU accounts

### Ease of read:

### Interactivity:

```{r interactivity_overall,echo=F,eval=T}
yearly_volume <- data.eu %>% group_by(tweet_year) %>% tally()

#all columns are saved as character to ensure homogeneity in earlier processes
#now we need a few things as numeric

data.eu<- data.eu %>% mutate(across(matches("is_*"),~as.numeric(.x)))

eu_interactions_summary<- data.eu %>%
  group_by(tweet_year) %>%
  summarise(yearly_retweet_share = (sum(is_retweet)),
            yearly_quote_share = (sum(is_quote)),
            yearly_reply_share = (sum(is_reply))) %>%
  left_join(x = .,y = yearly_volume, by = "tweet_year") %>% 
  mutate_at(vars(c("yearly_retweet_share","yearly_quote_share","yearly_reply_share")), ~(./n)) %>%
  pivot_longer(cols = starts_with("yearly_"),names_to = "variable",values_to = "share")

yearly_interactivity<- eu_interactions_summary %>%
  ggplot(data=.,aes(x = tweet_year, y = share)) +
  geom_bar(aes(fill = share),stat = "identity",position = "dodge")+theme_minimal()+
  facet_wrap(~variable)+
  labs(x = "Year",y = "Share",title = "EU verified accounts interactivity rate",subtitle = "N accounts = 115 \n N tweets = 1062742")

yearly_interactivity
```
```{r interactivity_actor_type, echo=F,eval=TRUE}
volume_by_type_year<- data.eu %>% group_by(Actor_type,tweet_year) %>% tally(name = "tweet_n")

act_type_interactivity<- data.eu %>%
  group_by(Actor_type,tweet_year) %>%
  summarise(yearly_retweet_share = (sum(is_retweet)),
            yearly_quote_share = (sum(is_quote)),
            yearly_reply_share = (sum(is_reply))) %>%
  left_join(x = .,y = volume_by_type_year, by = c("Actor_type","tweet_year")) %>% 
  mutate_at(vars(c("yearly_retweet_share","yearly_quote_share","yearly_reply_share")), ~(./tweet_n)) %>%
  pivot_longer(cols = starts_with("yearly_"),names_to = "variable",values_to = "share")

act_type_interactivity %>% ggplot(aes(x=tweet_year,y = share))+geom_bar(aes(fill = Actor_type),stat = "identity",position = "dodge")+theme_minimal()+facet_wrap(~variable)
```
**This is not a good graph**


### Political responsiblity reporting:

## Benchmarks: communication performance of the EU compared to IOs and national governments


### Ease of read

### Interactivity

### Political responsiblity reporting:


# Conclusion

# References